How it's been doing a statistics PhD plus some research

### 2022-02-01 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
Finish draft of these slides

* I'm interested in applied and methodological work
  * Applied: focus is on answering a question about the world
  * Methodological: focus is on developing techniques which can be used to answer questions about the world
* The deliniation between these might not be clear sometimes
  * To answer questions about the world you'll often have to develop new methods
  * To develop new (relevant) methods that you should be thinking about which questions they will allow you to answer to think
* Some examples of my work
  * Applied: estimating numbers of young women at risk
  * Methodological: investigating models for spatial smoothing

## Applied example

@@

```{r echo=FALSE}
knitr::include_graphics("depends/category-flowchart.pdf")
```

@@

## How impactful is this work

* Could be used to guide HIV interventions for women 15-29
  * Interventions suggested include STI-screening and treatment, economic empowerment, comprehensive sexuality education, PrEP, PEP
* Neglectedness, tractability, scale?
* TO-DO: Add the latest versions of infections averted graph

## Methods example

* TO-DO: Create annotated equations version of the Besag model

>>>>

* I'm interested in applied and methodological work
  * Applied: focus is on answering a question about the world
  * Methodological: focus is on developing techniques which can be used to answer questions about the world
* The deliniation between these might not be clear sometimes
  * To answer questions about the world you'll often have to develop new methods
  * To develop new (relevant) methods that you should be thinking about which questions they will allow you to answer to think
* Some examples of my work
  * Applied: estimating numbers of young women at risk
  * Methodological: investigating models for spatial structure

## Estimating numbers of young women at risk

@@

@@

```{r echo=FALSE}
knitr::include_graphics("depends/model-direct-benefits-h.pdf")
```

## The Besag model

$$
\phi_i \, | \, \bphi_{-i} \sim \N\left(\frac{\sum_{j: j \sim i} \phi_j}{n_{\delta i}}, \frac{1}{n_{\delta i}\tau_\phi}\right)
$$

Mean of $\phi_i$ average of adjacent units and precision is proportional to $n_{\delta i}$

```{r echo=FALSE}
knitr::include_graphics("geometry-graph-zwe.pdf")
```

## Impact of this work

* Could be used to guide HIV interventions for women 15-29
* Interventions suggested include 
  * STI-screening and treatment
  * Economic empowerment,
  * Comprehensive sexuality education
  * PrEP
  * PEP

```{r echo=FALSE}
knitr::include_graphics("depends/infections-averted-country.pdf")
```
